An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2013-02-04 Paper.tex
Removed separate reference to tech. appendix
Since I'm not using literate programming anymore, citing the software you
used in the paper seems tacky.  I'm taking it out.

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size $-\frac12$ on
    a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
    > 2$.
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k$ by $q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$, $\sup_t |\hat{B}_t^{*} - B^{*}| \to^p 0$, and $B^{*}
    = B + o_p$; $H_{t}$ is a sequence of $q$-vectors such that 
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s} & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s} & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s} & \text{fixed window} \\
      \end{cases}
    \end{equation}
    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, $h_s = h_s(\beta_0)$, and
    $\E h_{s} = 0$ for all $s$.
  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
    $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
    \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly
    finite in $t$, where $N$ is an open neighborhood of $\beta_{0}$.
  \item Each element of $\E f_{t}(\beta)$ is continuously
    differentiable in the neighborhood $N$.  Moreover, $\sup_{\beta
      \in N} | F_{t}(\beta) |$ is uniformly finite in $t$ with
    $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
  \item There exist finite constants $C$, $\phi > 0$, and $Q \geq r$
    such that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
    \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) - f_{t} \|_Q
    \leq C \epsilon^{\phi}\] and \[\sup_{\epsilon : N(\beta_{0},
      \epsilon) \subset N}\| \sup_{\beta \in N(\beta_{0}, \epsilon)}
    h_{t}(\beta) - h_{t} \|_Q \leq C \epsilon^{\phi},\] where
    $N(\beta, \epsilon) = \{b : |b - \beta| < \epsilon\}$.
  \item $R, P \to \infty$ as $T \to \infty$.
  \item $X_1^{*},\dots,X_T^{*}$ are generated by the moving blocks,
    circular blocks, or stationary bootstrap with block lengths drawn
    from the geometric distribution, and $b$ satisfies $b \to \infty$
    and $\frac{b}{P} \to 0$; $b$ is the block length of the moving or
    circular blocks bootstraps and is the expected block length of the
    stationary bootstrap.
  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
    uniformly positive definite.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T+1}))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

@@

\section{Monte Carlo Results}\label{sec:2}
I'll conduct two brief Monte Carlo experiments to demonstrate that
this paper's modified version of \citepos{ClW:07} statistic performs
similarly to their original test in the situations they
study.\footnote{All of these simulations were programmed in R
  \citep[version 2.14.0]{R} and use the \textsc{MASS} \citep[version
  info]{VeR:02}, xtable \citep[1.6-0]{Dah:09}, and dbframe
  \citep[version 0.2.1]{Cal:10b} packages.  For details on the
  programming, please see the supplemental appendix \citep{Cal:11f}.}
I'll use both of the \dgp s they consider as well as a modification to
study the performance of the statistics if there is instability.

>>>>

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size $-\frac12$ on
    a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
    > 2$.
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k$ by $q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$, $\sup_t |\hat{B}_t^{*} - B^{*}| \to^p 0$, and $B^{*}
    = B + o_p$; $H_{t}$ is a sequence of $q$-vectors such that 
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s} & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s} & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s} & \text{fixed window} \\
      \end{cases}
    \end{equation}
    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, $h_s = h_s(\beta_0)$, and
    $\E h_{s} = 0$ for all $s$.
  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
    $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
    \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly
    finite in $t$, where $N$ is an open neighborhood of $\beta_{0}$.
  \item Each element of $\E f_{t}(\beta)$ is continuously
    differentiable in the neighborhood $N$.  Moreover, $\sup_{\beta
      \in N} | F_{t}(\beta) |$ is uniformly finite in $t$ with
    $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
  \item There exist finite constants $C$, $\phi > 0$, and $Q \geq r$
    such that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
    \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) - f_{t} \|_Q
    \leq C \epsilon^{\phi}\] and \[\sup_{\epsilon : N(\beta_{0},
      \epsilon) \subset N}\| \sup_{\beta \in N(\beta_{0}, \epsilon)}
    h_{t}(\beta) - h_{t} \|_Q \leq C \epsilon^{\phi},\] where
    $N(\beta, \epsilon) = \{b : |b - \beta| < \epsilon\}$.
  \item $R, P \to \infty$ as $T \to \infty$.
  \item $X_1^{*},\dots,X_T^{*}$ are generated by the moving blocks,
    circular blocks, or stationary bootstrap with block lengths drawn
    from the geometric distribution, and $b$ satisfies $b \to \infty$
    and $\frac{b}{P} \to 0$; $b$ is the block length of the moving or
    circular blocks bootstraps and is the expected block length of the
    stationary bootstrap.
  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
    uniformly positive definite and $\E f_t(\beta_0) = \E
    f_s(\beta_0)$ for all $s$ and $t$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T+1}))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

@@

\section{Monte Carlo Results}\label{sec:2}
I'll conduct two brief Monte Carlo experiments to demonstrate that
this paper's modified version of \citepos{ClW:07} statistic performs
similarly to their original test in the situations they
study.\footnote{All of these simulations were programmed in R
  \citep[version 2.14.0]{R} and use the \textsc{MASS} \citep[version
  info]{VeR:02}, xtable \citep[1.6-0]{Dah:09}, and dbframe
  \citep[version 0.2.1]{Cal:10b} packages.}  I'll use both of the \dgp
s they consider as well as a modification to study the performance of
the statistics if there is instability.
